Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

\documentclass[conference]{configs/IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage[table,xcdraw]{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

% Please add the following required packages to your document preamble:
% 
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[]
	\begin{tabular}{llll}
		\rowcolor[HTML]{FFC702} 
		\textbf{Service/Operation} & \textbf{Baseline} & \textbf{Regression} & \textbf{Difference} \\
		inventory/write-cache & 63.1 ms & 368 ms  & +305 ms  \\
		inventory-db/update   & 1.75 ms & 2.26 ms & +0.51 ms \\
		memcached/set         & 4.94 ms & 4.71 ms & -0.23 ms \\
		inventory/update      & 15.2 ms & 14.8 ms & -0.47 ms \\
		inventory/db-update   & 32 ms   & 30.6 ms & -1.4 ms 
	\end{tabular}
\end{table}

>>>>

\documentclass[conference]{configs/IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
%\usepackage[table,xcdraw]{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\begin{table}[]
	\begin{tabular}{|l|l|l|l|}
		\hline
		\textbf{Service/Operation} & \textbf{Baseline} & \textbf{Regression} & \textbf{Difference} \\ \hline
		inventory/write-cache & 63.1 ms & 368 ms  & +305 ms  \\ \hline
		inventory-db/update   & 1.75 ms & 2.26 ms & +0.51 ms \\ \hline
		memcached/set         & 4.94 ms & 4.71 ms & -0.23 ms \\ \hline
		inventory/update      & 15.2 ms & 14.8 ms & -0.47 ms \\ \hline
		inventory/db-update   & 32 ms   & 30.6 ms & -1.4 ms  \\ \hline
	\end{tabular}
\end{table}
